---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
set.seed(1)
```

# ActionSquirrel

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

{ActionSquirrel} is an R package containing a (very work-in-progress) interactive visual experience ('game') in the R console, powered by [{R6}](https://r6.r-lib.org/). You play as the titular Action Squirrel. Move around and collect nuts for winter.

## How to play

### Install 

The package is available from GitHub.

```{r eval= FALSE}
install.packages("remotes")  # if not installed already
remotes::install_github("matt-dray/ActionSquirrel")
```

Attach the package for instructions.

```{r}
library(ActionSquirrel)
```

### Start

Initiate by assigning `ActionSquirrel$new()` to a name. This clears the console and generates a forest that contains Action Squirrel. And a delicious nut!

```{r}
x <- ActionSquirrel$new()
```

Note: neither Action Squirrel nor the nuts are as big as a tree. It's just perspective.

### Move

You control Action Squirrel. Use the `move()` method to move through the forest and grab the nuts.

```{r}
x$move("up")
```

Congratulations, your move tally has increased by one!

```{r}
x$move("left")
```

Congratulations, your nut tally has increased by one! And there's a new nut!

Did I mention there's sound effects? You'll have to play it to find out.

### Limits

Thinking of escape?

```{r}
x$move("up")
```
```{r}
x$move("up")
```

There is no escape!

## TODO

Proper gamification. See [the issues](https://github.com/matt-dray/ActionSquirrel/issues) and submit your own ideas.

## Thanks

Inspired in part by [Tomaz's 'Little Useless-Useful R Functions'](https://tomaztsql.wordpress.com/2021/09/13/little-useless-useful-r-functions-year-progress-bar/).

Thanks to Winston Chang for [the {R6} package](https://r6.r-lib.org/).

## Similar projects

I've done some other silly things with {R6}. You can:

* [play a text-based version of _Pokemon Blue_'s Safari Zone in R](https://www.rostrum.blog/2021/01/04/safar6/)
* [repay your loan to _Animal Crossing_'s Tom Nook with an Automatic Bell Dispenser](https://www.rostrum.blog/2020/04/04/repaying-tom-nook-with-r6/)
