---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ActionSquirrel

<!-- badges: start -->
[![Project Status: Concept – Minimal or no implementation has been done yet, or the repository is only intended to be a limited example, demo, or proof-of-concept.](https://www.repostatus.org/badges/latest/concept.svg)](https://www.repostatus.org/#concept)
<!-- badges: end -->

_Action Squirrel_ is a (very work-in-progress) interactive R-console experience ('game') made with [the {R6} package](https://r6.r-lib.org/).

## Install

Available from GitHub only.

```{r eval= FALSE}
install.packages("remotes")  # if not installed already
remotes::install_github("matt-dray/ActionSquirrel")
```

## How to play

Start with `ActionSquirrel$new()`. This will first clear the console.

```{r}
library(ActionSquirrel)
x <- ActionSquirrel$new()
```

Use the `move()` method to move Action Squirrel. Again, the console will first be cleared.

Go up!

```{r}
x$move("up")
```

Right!

```{r}
x$move("right")
```

Down!

```{r}
x$move("down")
```

Other right!

```{r}
x$move("left")
```

Note that Action Squirrel is not as big as a tree. It's just perspective.

## TODO

* Handle hard boundary
* Add random nut
* Tally nut points
* Add enemy
* Add timer/step count
* Play through seasons?
* Gamify properly

## Thanks

Inspired in part by [Tomaz's 'Little Useless-Useful R Functions'](https://tomaztsql.wordpress.com/2021/09/13/little-useless-useful-r-functions-year-progress-bar/).

Thanks to Winston Chang for [the {R6} package](https://r6.r-lib.org/).

## Similar projects

I've done some other silly things with {R6}. You can:

* [play a text-based version of _Pokemon Blue_'s Safari Zone in R](https://www.rostrum.blog/2021/01/04/safar6/)
* [repay your loan to _Animal Crossing_'s Tom Nook with an Automatic Bell Dispenser](https://www.rostrum.blog/2020/04/04/repaying-tom-nook-with-r6/)
